\documentclass[10pt]{article}
\usepackage[utf8]{inputenc}
\setlength{\arrayrulewidth}{1mm}
\usepackage{verbatim} 
\usepackage[dvipsnames]{xcolor}
\usepackage{ragged2e}
\usepackage[legalpaper, margin=0.35in,footskip = -0.6cm]{geometry}
\addtolength{\topmargin}{-0.3in}
\usepackage{titlesec}
\title{\LARGE{\textbf{\textit{VERONICA ANDRIAN}}}}
\author{\textbf{Email:} va1818@ic.ac.uk\quad $\cdotp$ \quad \textbf{Phone number:} +44 7379409006}
\date{}
\renewcommand{\baselinestretch}{0.8}

\definecolor{lightgrey}{RGB}{220, 220, 220}

\begin{document}
\sffamily
\maketitle
\titleformat{\section}
  {\normalfont\large\bfseries}{\thesection}{1em}{}[{\titlerule[0.7pt]}]
\thispagestyle{empty}

\vspace{-1.2cm}

\section*{\fontfamily{lmtt} \sffamily Education}
\vspace{-0.25cm}
\begin{center}
{{\fontfamily{lmtt}\colorbox{lightgrey}{\textbf{IMPERIAL COLLEGE LONDON (FIRST CLASS) } \quad \quad \qquad \quad \qquad \textbf{MEng Civil Engineering}  \quad \quad \quad \quad\quad\quad \quad \quad \quad \quad \quad \textbf{2018 - 2022}}}}

\end{center}
\vspace{-0.6cm}
\begin{itemize}
\setlength\itemsep{0.1em}
    \item Dean's List Award for Top 10\% (Top 8) of Year 3 and obtained a high 85\% in Fluid Mechanics module, 80\% in Transport Systems (both modules requires extensive mathematical modelling to real-life problems).
    \item Formulated a stochastic model of a naturally ventilated space and quantified the effects of stochasticity on the robustness of the system to flow reversal using stochastic calculus, Monte Carlo simulation, finite difference method and nonlinear dynamics.
    \item Formulated probabilistic dynamic programming to maintain optimal (minimal cost) release of water to the reservoir and  warehouse stock management strategy using Markov Chain. 
    \item Performed multinomial logit model and microeconomics utility theory to analyse travel mode choices, and performed market share forecasting to obtain direct and cross-elasticity.
    %\item Analyse the stress tensors of a dam using Finite Element Method (FEM) in ABAQUS, and analysed the discretisation error to ensure the reliability of the model. 
    \item Modeled indoor and outdoor spread of SARS-CoV-2 using analytical solution and numerical methods (Finite Difference Method) to solve advection-diffusion PDE.
    \item Designed automated window to maximise natural ventilation subject to thermal comfort range, showing analytical thinking and implementing technology in real-life problems.
    \item Led and organised a group of 5 to optimise the step-free access expansion of the London Underground Stations using mathematical modelling and visualisation of the network using Folium and NetworkX, obtaining over 80\% in grades.
\end{itemize}

\vspace{-0.6cm}
\begin{center}
{{\fontfamily{lmtt}\colorbox{lightgrey}{\textbf{CATS COLLEGE CANTERBURY }  \qquad  \qquad \quad  \quad \quad \quad \qquad \qquad \qquad \quad \quad \textbf{A-Level}\quad \qquad\quad \quad \qquad \qquad \qquad \qquad \quad \quad \quad \quad \textbf{2017 - 2018}}}}
\end{center}
\vspace{-0.6cm}
\begin{itemize}
\setlength\itemsep{0.1em}
    \item 3 A* in Mathematics, Further Mathematics and Chemistry, A in Physics.
    \item STEM Award in Mathematics, Further Mathematics and Physics for excellent performance, indicating strong numerical skills.
\end{itemize}

\section*{\sffamily Work Experience}
\vspace{-0.25cm}

\begin{comment}
\begin{center}
{{\fontfamily{lmtt}\colorbox{lightgrey}{\textbf{PIPELINE ENGINEER - SHELL UK ABERDEEN } \quad \quad\quad\quad \quad \quad \quad\quad\quad \quad\quad\quad\quad\quad \quad \quad \quad  \quad \quad \qquad\textbf{NOVEMBER 2022 - CURRENT}}}}
\end{center}
\begin{itemize}
    \item 
\end{itemize}
\end{comment}

\begin{center}
{{\fontfamily{lmtt}\colorbox{lightgrey}{\textbf{G10 STIR TRADING AND EQUITY QUANTS INTERN - UBS AG LONDON }  \qquad \qquad\quad\quad \quad \quad  \quad  \quad \quad \qquad\textbf{JUNE 2022 - AUGUST 2022}}}}
\end{center}
\vspace{-0.6cm}
\begin{itemize}
\setlength\itemsep{0.1em}
    \item Proposed a trading strategy using lag correlations in STIR Futures with potential profits of US\$ 160,000 in 2 months. 
    \item Learned the products the desk covers, FX Swaps, cross currency swaps, STIR Futures, how to price the products, the risk associated with each products and how to calculate the risk in terms of dv01.
    \item Learned to mark a yield curves, how to hedge their risks, and using different derivatives to take a view on the FX markets
    \item Work shadowed the FX Options Trading Desk, learned how the non-linearity in their FX products affect the dimensionality in the risk they take and need to subsequently hedge
    \item Used Random Forest and Neural Network to predict the price difference between Local Stochastic Vol and Local Vol model for DCN-KI single-asset exotic derivatives. 
    \item Learned and understand the Local Volatility and Local Stochastic Volatility model and how they are used to price exotics derivatives (i.e. path generation using Monte Carlo and calibration method).
    %\item Offered a graduate position within the FX Quants Desk
\end{itemize}

\vspace{-0.5cm}
\begin{center}
{{\fontfamily{lmtt}\colorbox{lightgrey}{\textbf{SOFTWARE DEVELOPER AND PRODUCT RESEARCH INTERN - INVESTEC UK }  \quad \qquad \qquad  \qquad \quad \qquad\textbf{JULY 2021 - SEPTEMBER 2021}}}}
\end{center}
\vspace{-0.6cm}
\begin{itemize}
\setlength\itemsep{0.1em}
    \item Work shadowed the FX Trading Team; Learned and understood options pricing theory (black-scholes model) and delta hedging.
    \item Analysed financial statement, evaluate the financial position, and provide investment recommendation to buy/hold/sell on Prada.
    \item Analysed industry competitors of Prada, and compare financial ratios, to further support buy/sell recommendations.
    \item Accelerated product research of their broker portal and deal automation by implementing linear programming and optimisation to their deal demographics.
    \item Developed proof of concept web-app for their new broker portal using ReactJS, C\#, which was learned in less than 2 weeks (includes creating API, search button functionality, etc.).
\end{itemize}

\begin{comment}
\begin{center}
{{\fontfamily{lmtt}\colorbox{lightgrey}{\textbf{VOLUNTEER TUTOR - IMPERIAL COLLEGE PIMLICO CONNECTION } \qquad   \quad \qquad \qquad \qquad\qquad \quad \qquad\textbf{OCTOBER 2019 - APRIL 2021}}}}
\end{center}
\begin{itemize}
    \item Taught Physics, Mathematics and Further Mathematics to Year 13 students who can't afford private tutoring.
    \item Developed excellent communication skills by breaking down difficult mathematical concepts to pre-university students.
\end{itemize}
\end{comment}

\vspace{-0.5cm}

\begin{center}
{{\fontfamily{lmtt}\colorbox{lightgrey}{\textbf{UNDERGRADUATE RESEARCHER - PROF. MICHAEL TEMPLETON} \quad \qquad \qquad \quad  \quad \quad \quad \quad \quad \quad \qquad \qquad  \quad \textbf{JULY 2020 - AUGUST 2020}}}}
\end{center}
\vspace{-0.6cm}
\begin{itemize}
\setlength\itemsep{0.1em}
    \item Perform data cleansing and extract trends from raw data, requiring strict attention to detail.
    \item Correlated water and sanitation facilities to the prevalence of Soil Transmitted Helminths in Ethiopia using Machine Learning algorithms such as Random Forest and Neural Network with over 85\% accuracy.
    \item Audited a course on Machine Learning by Stanford University through Coursera to prepare for this internship.
    %\item Due to the sensitive nature of these data, this information was dealt with a great level of discretion, proving experience dealing with confidential, sensitive information/case.
\end{itemize}

\begin{center}
{{\fontfamily{lmtt}\colorbox{lightgrey}{\textbf{UNDERGRADUATE RESEARCHER - DR. MARIOS CHRISTOU} \quad \quad \qquad \qquad \quad\quad \quad \quad \quad \quad \qquad \qquad \quad  \quad \textbf{FEBRUARY 2020 - JUNE 2020}}}}
\end{center}
\vspace{-0.6cm}
\begin{itemize}
\setlength\itemsep{0.1em}
    \item Managed the work during busy term-time with multiple projects, showing strong time management and multi-tasking skill.
    \item Analysed time-series wave data to prepare "good" wave data based on conditions derived from fluid mechanics principles.
    \item Learned to code in Python within a month to reasonably prepare for this research project, showing an ability to work in a pressurized environment.
\end{itemize}

\begin{comment}
\begin{center}
{{\fontfamily{lmtt}\colorbox{lightgrey}{\textbf{TEAM MEMBER - GAIL'S BAKERY LONDON } \quad \quad \qquad  \quad \quad \qquad \quad \quad \quad \quad \qquad \qquad \quad \quad  \qquad \quad \quad \qquad\textbf{NOVEMBER 2018 - MARCH 2019}}}}
\end{center}
\begin{itemize}
    \item Provide high-quality hospitality in a high-pressure, high-paced environment.
\end{itemize}
\end{comment}

\section*{\sffamily Notable Accomplishment}
\vspace{-0.1cm}
\begin{itemize}
\setlength\itemsep{0.1em}
    %\item \textbf{JP Morgan Investment Banking Virtual Experience}  (Participated via Forage, June 2020). Task includes: DCF Valuation and analysed potential companies for M\&A.
    \item \textbf{Singapore and Asian School Mathematics Olympiad in 2017}: Ranked in the Top 15\% across students in Asia.
    
    \item \textbf{University of Waterloo CEMC Cayley Mathematics Contest}: Ranked in the Top 25\% in 2017.
     \item \textbf{Singapore Mathematics Olympiad}: Participated in 2015.
    \item \textbf{Singapore and Asian School Mathematics Olympiad in 2014}: Ranked in the Top 10\% across students in Asia.
\end{itemize}

\section*{\sffamily Certification}
\vspace{-0.1cm}
\begin{itemize}
\setlength\itemsep{0.1em}
    \item Finance \& Quantitative Modelling for Analysts Specialization from the University of Pennsylvania via Coursera obtained on February 2022.
    \item Introduction to Corporate Finance from the University of Pennsylvania via Coursera obtained on June 2020.
    \item Achieved 95\% on Improving Deep Neural Network from DeepLearning.ai via Coursera obtained on June 2020.
    \item Achieved 91\% on Neural Network and Deep Learning from DeepLearning.ai via Coursera obtained on June 2020.
\end{itemize}



\end{document}
